
% Pradeep Garigipati's Resume
% Created: 14 Nov 2011
% Last Modified: 14 Nov 2011

\documentclass[11pt,oneside]{article}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\pagestyle{empty}
\geometry{letterpaper,tmargin=0.55in,bmargin=0.55in,lmargin=0.65in,rmargin=0.65in,headheight=0in,headsep=0in,footskip=.3in}
\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{Pradeep Garigipati}
\newcommand{\addr}{3902 College Main St., Apt 1510, Bryan, TX 77801}
\newcommand{\phone}{(713) 732-9156}
\newcommand{\email}{pradeep.garigipati@(tamu.edu/gmail.com)}
\newcommand{\web}{http://students.cse.tamu.edu/garigipp/}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

% This defines how the name looks
\newcommand{\bigname}[1]{
  \begin{center}\fontfamily{phv}\selectfont\Huge\scshape#1\end{center}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
  \vspace{4pt}
  {\fontfamily{phv}\selectfont\Large#1}
  \begin{itemize}
  \vspace{3pt}
}{
  \end{itemize}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
  \vspace{-4pt}
  \item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
  \vspace{-1pt}
  \item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[4]{
  \vspace{-5pt}
  \item
  \textbf{#1}, #2 \hfill #4\\
  \textit{#3}
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[4]{
  \resbigitem{#1}{#2}{#3}{#4}
  \vspace{-2pt}
  \begin{itemize}
}{
  \end{itemize}
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec2}[4]{
  \resbigitem{#1}{#2}{#3}{#4}
}
  
% This is a list that comes with a resbigitem
\newenvironment{ressubsec_variant}[2]{
  \resbigitem{#1}{#2}
  \vspace{-2pt}
  \begin{itemize}
}{
  \end{itemize}
}

% This is a simple sublist
\newenvironment{reslist}[1]{
  \resitem{\textbf{#1}}
  \vspace{-5pt}
  \begin{itemize}
}{
  \end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}
\fontfamily{ppl} \selectfont
% Name with horizontal rule
\bigname{\name}  
\begin{center} \web \end{center}
\vspace{-8pt} \rule{\textwidth}{1pt}
\vspace{-1pt} {\small\itshape \addr \hfill \phone; \email}
\vspace{8 pt}

{\fontfamily{phv}\selectfont\Large Objective}\\
Seeking a full time opportunity as a software development engineer.\\

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Education}
  \begin{ressubsec}{Texas A\&M University}{College Station, Texas}{Master of Science in Computer Science (GPA: 3.64)}{Graduation Date: May 2013}
    \ressubitem{Course Work: Computer Architecture, Algorithms \& Analysis, Parallel Computing, Geometric Modeling, Image Synthesis, Physics Based Simulation, Rendering \& Shading, and Image \& Video Processing.}
  \end{ressubsec}
%  \begin{ressubsec2}{Texas A\&M University}{College Station, Texas}{Master of Science in Computer Science (GPA: 3.64)}{Graduation Date: May 2013}
%    \end{ressubsec2}
  \begin{ressubsec2}{National Institute of Technology}{Durgapur, West Bengal, India.}{Bachelor of Technology in Computer Science and Engineering (GPA: 8.82/10)}{Graduation Date: May 2008}
  \end{ressubsec2}
\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Skills}

  \resitem{\textbf{Programming languages:} C/C++, Python, OpenGL, GLSL, RSL, Java, PL/SQL}
  \resitem{\textbf{Frameworks:} Qt, Cinder, Pthreads, MPI, CUDA}
  \resitem{\textbf{Web languages and frameworks:} HTML, CSS, J2EE Servlets, JavaScript}
  \resitem{\textbf{Server platforms:} WebSphere Application Server V6.1, Apache}
  \resitem{\textbf{Tools and Software:} Photoshop, HDR Shop, Matlab, \LaTeX{}}

\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%  
\begin{ressection}{Academic Projects}

  \begin{reslist}{Texas A\&M University}
      \ressubitem{Developed a Ray Tracing renderer with GUI interface.}
            \ressubitem{Created a physics based simulation of bird flight.}
      \ressubitem{Implemented a parallel algorithm to do Cholesky decomposition using MPI and CUDA.}
            \ressubitem{Studied and implemented swept volume generation for three dimensional surfaces.}
%      \ressubitem{Studied the concept of extent of generalization of APIs.}
  \end{reslist}

  \begin{reslist}{National Institute of Technology}
      \ressubitem{Designed a Java GUI application which assists in drawing Data Flow Diagrams.}
      \ressubitem{Developed an algorithm for bot-exploration on closed surfaces achieving a coverage of 59\%.}
  \end{reslist}
  
\end{ressection}  

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Work Experience}

  \begin{ressubsec2}{Visulization Department, Texas A\&M University}{College Station, TX}{Research Assistant}{September 2012 - Present}
  \end{ressubsec2}

   \begin{ressubsec2}{USC Institute of Creative Technologies}{Playa Vista, CA}{Visiting Research Assistant}{May 2012 - July 2012}
   \end{ressubsec2}

  \begin{ressubsec2}{Open Access Labs, Texas A\&M University}{College Station, TX}{Student Worker}{September 2011-April 2012}
  \end{ressubsec2}

  \begin{ressubsec2}{Tata Consultancy Services Limited}{Mumbai, India}{Assistant Systems Engineer}{July 2008-June 2010}
  \end{ressubsec2}

\end{ressection}


\newpage


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Publications}
	\resitem{Pradeep Garigipati, Ergun Akleman: Duotone Surfaces. International Symposium on Computational Aesthetics in Graphics, Visualization, and Imaging, 2012. Annecy, France. 99-106.}
	\resitem{Yufeng Zhu, Pradeep Garigipati, Pieter Peers, Paul Debevec and Abhijeet Ghosh. Estimating Diffusion Parameters from Polarized Spherical GradientIllumination. IEEE Computer Graphics and Applications, 2013(To Appear).}
\end{ressection}



%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Achievements and Activities}
  
%  \resitem{Contributed to the research work: 'Estimating Diffusion Parameters From Polarized Spherical Gradient Illumination', which was presented at SIGGRAPH 2012 Talks/Posters.}
  \resitem{Completed IBM Certification as System Administrator, WebSphere Application Server Network Deployment V6.1.}
  \resitem{Completed Green Belt Certification in Six Sigma.}
  
\end{ressection}
\end{document}
